Price of Anarchy for Mean Field Games

### 2018-07-29 PoA.tex
only cite Proposition 2 in Proposition 3, to be consistent throughout Propositions 4-7

	From equation (\ref{eq:v_t_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$: 
	$$	\lim_{r\to \infty} v^r_t = Var(\xi)e^{2b_1 t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{r \to \infty}_t.
	$$
	The variance function $v_t^{r}$ is also uniformly bounded over $t \in [0,T]$. We also have $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
	\begin{equation*}
		\lim_{r \to \infty} SC^{MKV,r} = \frac{1}{2} \left( \int_0^T (q+\bar{q}) v^{r \to \infty}_t dt + (q_T + \bar{q}_T) v^{r\to \infty}_T + w^{r \to \infty}_0 (\mathbb{E}(\xi))^2 \right)  >0.
	\end{equation*}
	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ_new_notation}), we have 
	$$\displaystyle \lim_{r \to \infty} PoA^r = 1.$$

@@

	From equation (\ref{eq:v_t_new_notation}) and the bounded convergence theorem, for each $t \in [0,T]$:
	$$ \lim_{b_2 \to 0}v_t^{b_2}=Var(\xi) e^{2b_1 t} + \sigma^2 \int_0^t e^{2b_1 (t-s)} ds=:v_t^{b_2 \to 0}>0,$$
	and thus, $ 0 < \lim_{b_2 \to 0} SC^{MKV,b_2} < \infty.$
	Therefore, combined with equation (\ref{eq:PoA_LQ_new_notation}), we conclude that: $$\lim_{b_2 \to 0} PoA^{b_2} =: PoA^{b_2 \to 0} > 1.$$
\end{proof}

>>>>

	From equation (\ref{eq:v_t_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$: 
	$$	\lim_{r\to \infty} v^r_t = Var(\xi)e^{2b_1 t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{r \to \infty}_t.
	$$
	The variance function $v_t^{r}$ is also uniformly bounded over $t \in [0,T]$. We also have $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
	\begin{equation*}
		\lim_{r \to \infty} SC^{MKV,r} = \frac{1}{2} \left( \int_0^T (q+\bar{q}) v^{r \to \infty}_t dt + (q_T + \bar{q}_T) v^{r\to \infty}_T + w^{r \to \infty}_0 (\mathbb{E}(\xi))^2 \right)  >0.
	\end{equation*}
	Therefore, from equation (\ref{eq:PoA_LQ_new_notation}), we have 
	$$\displaystyle \lim_{r \to \infty} PoA^r = 1.$$

@@

	From equation (\ref{eq:v_t_new_notation}) and the bounded convergence theorem, for each $t \in [0,T]$:
	$$ \lim_{b_2 \to 0}v_t^{b_2}=Var(\xi) e^{2b_1 t} + \sigma^2 \int_0^t e^{2b_1 (t-s)} ds=:v_t^{b_2 \to 0}>0,$$
	and thus, $ 0 < \lim_{b_2 \to 0} SC^{MKV,b_2} < \infty.$ We conclude $\lim_{b_2 \to 0} PoA^{b_2} =: PoA^{b_2 \to 0} > 1.$
\end{proof}
